Thesis outline

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/GV.tex
Fixed typos

% Feedback from AGN (strongly affects massive galaxies)
% Feedback from SN (dominates feedback in dwarfs)
% gas stripping interactions
% tidally-triggered star formation
There are a number of different astrophysical processes which simultaneously 
evolve a galaxy's stellar and gas content.  AGN feedback strongly affects 
massive galaxies, while dwarf galaxy feedback is dominated by supernovae.  Both 
AGN and supernovae can inject enough energy into a galaxy's ISM to prevent its 
cooling, thereby quenching star formation.  In addition to internal mechanisms, 
galaxies will often experience interactions in denser environmental regions.  
Depending on the properties of the galaxies involved (mass, speed, etc.), these 
interactions can either strip gas from the galaxy (removing a primary source of 
fuel for future star formation), or they can trigger a burst of star formation.

@@

A galaxy's color is a logarithmic ratio of the ratio of the flux emitted by the 
galaxy in two different bands.  The stellar population of a galaxy will 
determine its color: redder galaxies contain much older, cooler stars, while the 
spectrum of a bluer galaxy is produced by light from much younger, hotter stars.  
While the KIAS-VAGC catalog (described below in Section \ref{sec:SDSS}) provides 
the $u-r$ color for all galaxies in SDSS, we make use of the Petrosian fluxes in 
the NSA (described in Section \ref{sec:GALEX}) to calculate the UV--optical 
color.  The NUV$-r$ color is calculated by
\begin{equation}
    \text{NUV}-r = -2.5\log \left( \frac{f_{NUV}}{f_r} \right)
\end{equation}
where $f_{NUV}$ is the Petrosian flux in the NUV-band of GALEX, and $f_r$ is the 
Petrosian flux in the $r$-band of SDSS.

@@

We use the photometric data from SDSS (optical) and GALEX (ultraviolet) as 
cross-matched in the NSA.

\subsection{Optical data --- SDSS}\label{sec:SDSS}
% Should we use NSA for abs. mag. instead? - yes, but not for the thesis

The SDSS Data Release 7 \citep[DR7;][]{Abazajian09} is a wide-field multi-band 
imaging and spectroscopic survey that uses drift scanning to map approximately 
one-quarter of the northern sky.  A dedicated 2.5-meter telescope at the Apache 
Point Observatory in New Mexico takes photometric data in the five-band SDSS 
system --- $u$, $g$, $r$, $i$, and $z$ \citep{Fukugita96,Gunn98}.  Galaxies with 
a Petrosian $r$-band apparent magnitude $m_r < 17.77$ are selected for 
spectroscopic analysis \citep{Lupton01,Strauss02}.  Gas-phase chemical 
abundances are calculated via the Direct $T_e$ method using emission-line fluxes 
measured by the MPA-JHU catalog\footnote{Available at 
\url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in 
\cite{Douglass17c}.  The large-scale environment of the galaxies is based on the 
void catalog compiled by \cite{Pan12}.  This void catalog is constructed from 
SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  Galaxies which are 
located within the identified voids are labeled as void galaxies; those which do 
not reside in a void are designated as wall galaxies.  Because the minimum 
diameter of a void is defined as 10 \hMpc , the large-scale environment of 
galaxies within 5 \hMpc of the edge of the SDSS DR7 footprint cannot be 
described, so their environment is labeled as unknown.

% KIAS-VAGC (morphological classification)
The Korea Institute for Advanced Study Value-Added Galaxy Catalog 
\citep[KIAS-VAGC;][]{Choi10} contains galaxies from the SDSS DR7 main sky survey 
based on the New York University Value-Added Galaxy Catalog Data Release 7 
\citep[NYU-VAGC;][]{Blanton05}.  It provides a morphological class and type 
following the automated morphology classification scheme of \cite{Park05}, using 
the color $u-r$, color gradient $\Delta (g-r)$, and inverse concentration index.  
With these three quantities, galaxies are separated into one of three different 
morphological types: normal late type, normal early type, blue early type, and 
one of two different morphological classes: elliptical or lenticular and spiral 
or irregular.  For reference, typical star-forming spiral galaxies would be 
classified as a normal late type spiral or irregular galaxy, star-forming dwarf 
galaxies are usually normal late type spiral or irregular galaxies, and red 
elliptical galaxies are typically classified as normal early type elliptical or 
lenticular galaxies.  We use the absolute magnitudes as listed in the KIAS-VAGC.

\subsection{UV data --- GALEX}\label{sec:GALEX}
The Galaxy Evolution Explorer \citep[GALEX]{Martin05} is an orbiting space 
telescope conducting an extra-galactic ultraviolet all-sky survey.  The 
instrument allows imaging and spectroscopic observations in two ultraviolet 
bands: Far UV (FUV, 1350--1780\AA) and Near UV (NUV, 1770--2730\AA) 
\citep{Morrissey07}.  The NUV-$r$ colors used in this study are calculated from 
the azimuthally-averaged SDSS-style Petrosian fluxes provided in the NASA-Sloan 
Atlas version 0.1.2 \citep[NSA]{Blanton11}.

@@

% CMD in NUV-r, showing where green valley galaxies live
\begin{figure}
    \includegraphics[width=0.75\textwidth]{Images/GV/NUVr_CMD_3pop_scatter}
    \caption[NUV-$r$ color-magnitude diagram of SDSS galaxies]{The NUV$-r$ 
    color-magnitude diagram of galaxies in SDSS DR7.  Those galaxies in the red 
    contours have morphological classifications of either normal early types 
    (aimc $=1$) or blue early types (aimc $=2$), as determined by the KIAS-VAGC.  
    The green points represent a subset of the normal late type galaxies (aimc 
    less than 25, excluding those with values of 1 or 2), and the blue contours 
    represents the remaining normal late type galaxies (aimc greater than 25).  
    It is clear that this morphological classification defines those galaxies 
    that are transitioning from the blue sequence to the red cloud.}
    \label{fig:NUVr_CMD}
\end{figure}

@@

% Histogram of NUV-r, with all, red, blue, green galaxies (aimc values)
\begin{figure}
    \includegraphics[width=0.75\textwidth]{Images/GV/NUVr_CMDclassifications}
    \caption[Distribution of NUV-$r$ of SDSS galaxies]{A histogram of the 
    NUV$-r$ color of those SDSS DR7 galaxies which are also detected in GALEX.  
    The red cloud, blue sequence, and green valley populations are separated by 
    the morphological types as defined by the KIAS-VAGC.  It is readily apparent 
    that the green valley galaxies exist in the space between the red cloud and 
    blue sequence.}
    \label{fig:NUVr_hist}
\end{figure}

This analysis reveals a population of galaxies that lie in the Green Valley on 
the NUV$-r$ color-magnitude diagram, identified independent of their location on 
the diagram.  Rather than being classified based on arbitrary limits placed on 
the NUV$-r$ values \citep[as done by][]{Schawinski14,Salim14a}, the galaxies can 
be easily separated into three distinct populations based on the galaxies' 
morphological types as calculated in the KIAS-VAGC; this can be seen in Fig. 
\ref{fig:NUVr_CMD}.  Here, we group together normal late type and blue early 
type galaxies, and we separate into two groups the normal late type galaxies 
based on their value of the morphological type quantity calculated in the 
KIAS-VAGC.  Defined by the $u-r$ color and the color gradient $\Delta (g-i)$, it 
is novel that an estimate of the morphological type of the galaxies is an 
adequate classification for the three populations of the NUV$-r$ CMD.  In 
addition, Fig. \ref{fig:NUVr_hist} shows a histogram of the galaxies which 
overlap in both GALEX and SDSS, separated by their morphological classification 
from the KIAS-VAGC.  It shows that the three populations are well fit by three 
Gaussians --- the new population in the middle is the transient galaxy 
population originally ``missing'' from the optical CMD.

@@

If the green valley galaxies represent those galaxies transitioning between the 
blue sequence and red cloud, then their stellar masses should overlap the masses 
in both these populations.  The distribution of the stellar masses for the 
galaxies in SDSS DR7 is shown in Fig. \ref{fig:M_hist}.  We can see that the 
galaxies in the green valley have stellar masses comparable to those in the red 
cloud.  The stellar masses of those galaxies in the blue sequence range from the 
lowest mass objects up through the stellar masses of the green valley galaxies.  
The distribution of stellar masses of blue sequence galaxies should be much 
broader than the range of masses seen in the red cloud galaxies, since those in 
the blue sequence are slowly building up their stellar mass by forming stars 
from both their gas reservoirs and cool gas falling onto the galaxy.  Galaxies 
in the red cloud are fairly stagnant in their star formation, so the range of 
stellar masses of these galaxies will be more narrow than that of the blue 
sequence.  If the green valley galaxies are transitioning between the two 
populations due to a quenching of star formation or a sudden burst of star 
formation, then we would expect their mass range to cover the high-mass end of 
the blue sequence and most of the red cloud.  These expectations are met in Fig. 
\ref{fig:M_hist}.

@@

% Histogram of metallicity for red, blue, green galaxies
\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/GV/Z12logOH_I06relations_t3}
    \includegraphics[width=0.49\textwidth]{Images/GV/N12logNH_I06relations_t3}
    \includegraphics[width=0.49\textwidth]{Images/GV/logNO_I06relations_t3}
    \caption[Distribution of gas-phase chemical abundances in cross-matched SDSS 
    DR7 -- GALEX galaxies]{Histograms of the oxygen abundance (top left), 
    nitrogen abundance (top right), and N/O ratio (bottom center) of the 
    cross-matched SDSS DR7 -- GALEX galaxies, separated into their locations on 
    the NUV$-r$ color-magnitude diagram according to the morphological type 
    listed in the KIAS-VAGC.  It is readily apparent that the green valley 
    galaxies have higher nitrogen abundances than those in the blue sequence 
    (and some of the red cloud).  This, therefore, corresponds to them having 
    high N/O ratios.}
    \label{fig:Z_hist}
\end{figure}

@@

When we separate the galaxies in each of the three populations by their 
large-scale environment, we discover a variation in these populations as a 
function of luminosity.  As we see in Fig. \ref{fig:Mr_bin}, the fraction of 
galaxies in the green valley depends on the large-scale environment, even at 
fixed stellar mass or luminosity.  A larger fraction of faint wall galaxies are 
found in the green valley than for faint void galaxies.

@@

\section[GV galaxy properties]{Understanding green valley galaxies}\label{sec:discussion_GV}

Galaxies in the green valley are described to be in a transitional period of the 
galaxy's life cycle, where they are being quenched in their star formation or 
are beginning to form stars after being quiescent.  Here, we are able to 
quantitatively define galaxies in the green valley of the UV-optical CMD.  We 
find them to be of comparable stellar mass to galaxies in the red cloud, have 
intermediate SFRs and intermediate-to-low sSFRs, and have higher gas-phase 
nitrogen abundances and N/O ratios than galaxies in the blue sequence.

@@

As explained in \cite{Douglass17b}, nitrogen is thought to be produced in both a 
primary and secondary stage, depending on the presence of other heavy elements.  
The fact that the galaxies in the green valley have higher nitrogen abundances 
compared to those in the blue sequence indicate that they are building up a 
surplus of nitrogen, most likely due to the presence of heavier elements in 
later episodes of star formation.  The surplus of heavier elements allows the 
CNO cycle to commence earlier in the stars' lifetimes, producing nitrogen at a 
higher rate than oxygen.  It is also possible that the higher nitrogen 
abundances are a sign that the galaxies' intermediate mass stars (those 
primarily responsible for nitrogen synthesis) have expired.  This surplus of 
nitrogen results in the high N/O ratios seen for the green valley galaxies in 
Fig. \ref{fig:Z_hist}.

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/GV/1sig_all_BPT_t3_12logOHrelations_dust_hist}
    \includegraphics[width=0.49\textwidth]{Images/GV/1sig_all_BPT_t3_12logNHrelations_dust_hist}
    \includegraphics[width=0.49\textwidth]{Images/GV/1sig_all_BPT_t3_logNOrelations_dust_hist}
    \caption[Gas-phase chemical abundance distributions for star-forming, 
    composite, and AGN galaxies]{Distribution of the gas-phase oxygen abundance 
    (O/H, top left), nitrogen abundance (N/H, top right), and N/O ratio (bottom 
    center) of the SDSS DR7 galaxies with detectable emission lines for 
    abundance calculations with the Direct $T_e$ method.  Star-forming galaxies 
    are shown with a solid cyan line, while composite galaxies are a dashed 
    orange line and galaxies with an AGN are represented as a dotted magenta 
    line.  Composite galaxies have lower oxygen abundances than both 
    star-forming galaxies and those with an AGN.  The nitrogen abundance range 
    is different for each of the three classes, with star-forming galaxies 
    having the lowest nitrogen abundances, AGN having the highest, and 
    composite galaxies in the middle.  Therefore, star-forming galaxies have 
    N/O ratios $< 0$, while composite galaxies and galaxies with an AGN have 
    N/O ratios between -1 and 0.5.}
    \label{fig:BPT_abund}
\end{figure}

@@

Based on our analysis, green valley galaxies have stellar masses comparable to 
those in the red cloud.  They have intermediate SFRs, and low-to-intermediate 
sSFRs.  Green valley galaxies also have high gas-phase nitrogen abundances (N/H), 
resulting in high N/O ratios.  While their SFRs show that something has quenched 
their star formation, their stellar masses inform us that this is not due to any 
premature quenching mechanism.  The high nitrogen abundances in the green valley 
galaxies indicate that the galaxies are either no longer forming stars (since 
nitrogen is produced in lower mass stars than oxygen), or that the galaxies were 
able to produce both primary and secondary nitrogen (heavy elements were present 
during the last few star formation episodes to permit the CNO cycle to commence 
earlier).  This chemical abundance pattern (normal oxygen, high nitrogen, and 
high N/O ratio) is also seen in galaxies classified as AGN, indicating that the 
galaxies in the green valley have an AGN.

There is a higher fraction of faint wall galaxies than faint void galaxies in 
the green valley.  In conjunction with the conclusions of \cite{Douglass17b} and 
\cite{Douglass17c}, this indicates that void dwarf galaxies are less evolved 
than dwarf galaxies in denser environments.  It would be beneficial to 
investigate the small-scale ($\sim$1 \hMpc) environment of galaxies in the green 
valley, to determine if any interactions are responsible for the transitional 
state.

>>>>

% Feedback from AGN (strongly affects massive galaxies)
% Feedback from SN (dominates feedback in dwarfs)
% gas stripping interactions
% tidally-triggered star formation
There are a number of different astrophysical processes which simultaneously 
evolve a galaxy's stellar and gas content.  Active galactic nuclei (AGN) 
feedback strongly affects massive galaxies, while dwarf galaxy feedback is 
dominated by supernovae.  Both AGN and supernovae can inject enough energy into 
a galaxy's ISM to prevent its cooling, thereby quenching star formation.  In 
addition to internal mechanisms, galaxies in denser environmental regions will 
often experience interactions.  Depending on the properties of the galaxies 
involved (mass, speed, etc.), these interactions can either strip gas from the 
galaxy (removing a primary source of fuel for future star formation), or they 
can trigger a burst of star formation.

@@

A galaxy's color is a logarithmic ratio of the flux emitted by the galaxy in two 
different bands.  The stellar population of a galaxy will determine its color: 
red galaxies contain much older, cooler stars, while the spectrum of a blue 
galaxy is produced by light from much younger, hotter stars.  While the 
KIAS-VAGC catalog (described below in Section \ref{sec:SDSS}) provides the $u-r$ 
color for all galaxies in SDSS, we make use of the Petrosian fluxes in the NSA 
(described in Section \ref{sec:GALEX}) to calculate the UV--optical color.  The 
NUV$-r$ color is calculated by
\begin{equation}
    \text{NUV}-r = -2.5\log \left( \frac{f_{NUV}}{f_r} \right)
\end{equation}
where $f_{NUV}$ is the Petrosian flux in the NUV-band of GALEX, and $f_r$ is the 
Petrosian flux in the $r$-band of SDSS.

@@

We use the photometric data from SDSS (optical) and GALEX (ultraviolet) as 
cross-matched in the NASA-Sloan Atlas\footnote{\url{http://www.nsatlas.org}} 
(NSA).

\subsection{Optical data: SDSS}\label{sec:SDSS}
% Should we use NSA for abs. mag. instead? - yes, but not for the thesis

The SDSS Data Release 7 \citep[DR7;][]{Abazajian09} is a wide-field multi-band 
imaging and spectroscopic survey that uses drift scanning to map approximately 
one-quarter of the northern sky.  A dedicated 2.5-meter telescope at the Apache 
Point Observatory in New Mexico takes photometric data in the five-band SDSS 
system --- $u$, $g$, $r$, $i$, and $z$ \citep{Fukugita96,Gunn98}.  Galaxies with 
a Petrosian $r$-band apparent magnitude $m_r < 17.77$ are selected for 
spectroscopic analysis \citep{Lupton01,Strauss02}.  Gas-phase chemical 
abundances are calculated via the Direct $T_e$ method using emission-line fluxes 
as measured in the MPA-JHU catalog\footnote{Available at 
\url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in 
\cite{Douglass17c}.  The large-scale environment of the galaxies is based on the 
void catalog compiled by \cite{Pan12}.  This void catalog is constructed from 
SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  Galaxies which are 
located within the identified voids are labeled as void galaxies; those which do 
not reside in a void are designated as wall galaxies.  Because the minimum 
diameter of a void is defined as 10 \hMpc , the large-scale environment of 
galaxies within 5 \hMpc of the edge of the SDSS DR7 footprint cannot be 
described, and so their environment is labeled as unknown.

% KIAS-VAGC (morphological classification)
The Korea Institute for Advanced Study Value-Added Galaxy Catalog 
\citep[KIAS-VAGC;][]{Choi10} contains galaxies from the SDSS DR7 main sky survey 
based on the New York University Value-Added Galaxy Catalog Data Release 7 
\citep[NYU-VAGC;][]{Blanton05}.  It provides a morphological class and type 
following the automated morphology classification scheme of \cite{Park05}, using 
the color $u-r$, color gradient $\Delta (g-r)$, and inverse concentration index.  
With these three quantities, galaxies are separated into one of three different 
morphological types: normal late type, normal early type, or blue early type, 
and one of two different morphological classes: elliptical or lenticular and 
spiral or irregular.  For reference, typical star-forming spiral galaxies are 
classified as normal late type spiral or irregular galaxies, star-forming dwarf 
galaxies are usually normal late type spiral or irregular galaxies, and red 
elliptical galaxies are typically classified as normal early type elliptical or 
lenticular galaxies.  We use the absolute magnitudes as listed in the KIAS-VAGC.

\subsection{UV data: GALEX}\label{sec:GALEX}
The Galaxy Evolution Explorer \citep[GALEX;][]{Martin05} is an orbiting space 
telescope conducting an extra-galactic ultraviolet all-sky survey.  The 
instrument allows imaging and spectroscopic observations in two ultraviolet 
bands: Far UV (FUV, 1350--1780\AA) and Near UV (NUV, 1770--2730\AA) 
\citep{Morrissey07}.  The NUV-$r$ colors used in this study are calculated from 
the azimuthally-averaged SDSS-style Petrosian fluxes provided in the NSA version 
0.1.2 \citep{Blanton11}.

@@

% CMD in NUV-r, showing where green valley galaxies live
\begin{figure}
    \includegraphics[width=0.75\textwidth]{Images/GV/NUVr_CMD_3pop_scatter}
    \caption[NUV-$r$ color-magnitude diagram of NSA galaxies]{The NUV$-r$ 
    color-magnitude diagram of galaxies in the NSA.  Those galaxies in the red 
    contours have morphological classifications of either normal early types 
    (aimc $=1$) or blue early types (aimc $=2$), as determined by the KIAS-VAGC.  
    The green points represent a subset of the normal late type galaxies (aimc 
    less than 25, excluding those with values of 1 or 2), and the blue contours 
    represent the remaining normal late type galaxies (aimc greater than 25).  
    It is clear that this morphological classification defines those galaxies 
    that are transitioning from the blue sequence to the red cloud.}
    \label{fig:NUVr_CMD}
\end{figure}

@@

% Histogram of NUV-r, with all, red, blue, green galaxies (aimc values)
\begin{figure}
    \includegraphics[width=0.75\textwidth]{Images/GV/NUVr_CMDclassifications}
    \caption[Distribution of NUV-$r$ for SDSS galaxies]{A histogram of the 
    NUV$-r$ color of those SDSS DR7 galaxies which are also detected in GALEX.  
    The red cloud, blue sequence, and green valley populations are separated by 
    the morphological types as defined by the KIAS-VAGC.  It is readily apparent 
    that the green valley galaxies exist in the space between the red cloud and 
    blue sequence.}
    \label{fig:NUVr_hist}
\end{figure}

This analysis reveals a population of galaxies that lie in the green valley on 
the NUV$-r$ color-magnitude diagram, identified independent of their location on 
the diagram.  Rather than being classified based on arbitrary limits placed on 
the NUV$-r$ values \citep[as done by][]{Schawinski14,Salim14a}, the galaxies can 
be easily separated into three distinct populations based on the galaxies' 
morphological types as calculated in the KIAS-VAGC; this can be seen in Fig. 
\ref{fig:NUVr_CMD}.  Here, we group together normal late type and blue early 
type galaxies, and we separate into two groups the normal late type galaxies 
based on their value of the morphological type quantity calculated in the 
KIAS-VAGC.  Defined by the $u-r$ color and the color gradient $\Delta (g-i)$, it 
is novel that an estimate of the morphological type of the galaxies is an 
adequate classification for the three populations of the NUV$-r$ CMD.  In 
addition, Fig. \ref{fig:NUVr_hist} shows a histogram of the galaxies which 
overlap in both GALEX and SDSS, separated by their morphological classification 
from the KIAS-VAGC.  It shows that the three populations are well fit by three 
Gaussians --- the new population in the middle is the transient galaxy 
population originally ``missing'' from the optical CMD.

@@

If the green valley galaxies represent those galaxies transitioning between the 
blue sequence and the red cloud, then their stellar masses should overlap the 
masses in both these populations.  The distribution of the stellar masses for 
the galaxies in SDSS DR7 is shown in Fig. \ref{fig:M_hist}.  We can see that the 
galaxies in the green valley have stellar masses comparable to those in the red 
cloud.  The stellar masses of those galaxies in the blue sequence range from the 
lowest mass objects up through the stellar masses of the green valley galaxies.  
The distribution of stellar masses of blue sequence galaxies should be much 
broader than the range of masses seen in the red cloud galaxies, since those in 
the blue sequence are slowly building up their stellar mass by forming stars 
from both their gas reservoirs and cool gas falling onto the galaxy.  Galaxies 
in the red cloud are fairly stagnant in their star formation, so the range of 
stellar masses of these galaxies will be more narrow than that of the blue 
sequence.  If the green valley galaxies are transitioning between the two 
populations due to a quenching of star formation or a sudden burst of star 
formation, then we would expect their mass range to cover the high-mass end of 
the blue sequence and most of the red cloud.  These expectations are met in Fig. 
\ref{fig:M_hist}.

@@

% Histogram of metallicity for red, blue, green galaxies
\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/GV/Z12logOH_I06relations_t3}
    \includegraphics[width=0.49\textwidth]{Images/GV/N12logNH_I06relations_t3}
    \includegraphics[width=0.49\textwidth]{Images/GV/logNO_I06relations_t3}
    \caption[Distribution of abundances in cross-matched SDSS DR7 -- GALEX 
    galaxies]{Histograms of the oxygen abundance (top left), nitrogen abundance 
    (top right), and N/O ratio (bottom center) of the cross-matched SDSS DR7 -- 
    GALEX galaxies, separated by their locations on the NUV$-r$ color-magnitude 
    diagram according to the morphological type listed in the KIAS-VAGC.  It is 
    readily apparent that the green valley galaxies have higher nitrogen 
    abundances than those in the blue sequence (and some of the red cloud).  
    This, therefore, corresponds to them having high N/O ratios.}
    \label{fig:Z_hist}
\end{figure}

@@

When we separate the galaxies in each of the three populations by their 
large-scale environment, we discover a variation in these populations as a 
function of luminosity.  As we see in Fig. \ref{fig:Mr_bin}, the fraction of 
galaxies in the green valley depends on the large-scale environment, even at 
fixed stellar mass or luminosity.  There is a larger fraction of faint wall 
galaxies than faint void galaxies in the green valley.

@@

\section[Understanding GV galaxies]{Understanding green valley galaxies}\label{sec:discussion_GV}

Galaxies in the green valley are thought to be in a transitional period of the 
galaxy's life cycle, where their star formation is quenching or they are 
beginning to form stars after a quiescent period.  Here, we are able to 
quantitatively define galaxies in the green valley of the UV-optical CMD.  We 
find them to be of comparable stellar mass to galaxies in the red cloud, have 
intermediate SFRs and intermediate-to-low sSFRs, and have higher gas-phase 
nitrogen abundances and N/O ratios than galaxies in the blue sequence.

@@

As explained in \cite{Douglass17b}, nitrogen is thought to be produced in both a 
primary and secondary stage depending on the presence of other heavy elements.  
When compared to those in the blue sequence, the higher nitrogen abundances of 
galaxies in the green valley indicate that green valley galaxies are building up 
a surplus of nitrogen, most likely due to the presence of heavier elements in 
later episodes of star formation.  The surplus of these heavier elements allows 
the CNO cycle to commence earlier in the stars' lifetimes, producing nitrogen at 
a higher rate than oxygen.  It is also possible that the higher nitrogen 
abundances are a sign that the galaxies' intermediate mass stars (those 
primarily responsible for nitrogen synthesis) have expired.  This surplus of 
nitrogen results in the high N/O ratios seen for the green valley galaxies in 
Fig. \ref{fig:Z_hist}.

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/GV/1sig_all_BPT_t3_12logOHrelations_dust_hist}
    \includegraphics[width=0.49\textwidth]{Images/GV/1sig_all_BPT_t3_12logNHrelations_dust_hist}
    \includegraphics[width=0.49\textwidth]{Images/GV/1sig_all_BPT_t3_logNOrelations_dust_hist}
    \caption[Abundance distributions for star-forming, composite, and AGN 
    galaxies]{Distribution of the gas-phase oxygen abundance (O/H, top left), 
    nitrogen abundance (N/H, top right), and N/O ratio (bottom center) of the 
    SDSS DR7 galaxies with detectable emission lines for abundance calculations 
    with the Direct $T_e$ method.  Star-forming galaxies are shown with a solid 
    cyan line, while composite galaxies are a dashed orange line and galaxies 
    with an AGN are represented as a dotted magenta line.  Composite galaxies 
    have lower oxygen abundances than both star-forming galaxies and those with 
    an AGN.  The nitrogen abundance range is different for each of the three 
    classes, with star-forming galaxies having the lowest nitrogen abundances, 
    AGN having the highest, and composite galaxies in the middle.  Therefore, 
    star-forming galaxies have N/O ratios $< 0$, while composite galaxies and 
    galaxies with an AGN have N/O ratios between -1 and 0.5.}
    \label{fig:BPT_abund}
\end{figure}

@@

Based on our analysis, green valley galaxies have stellar masses comparable to 
those in the red cloud.  They have intermediate SFRs, and low-to-intermediate 
sSFRs.  Green valley galaxies also have high gas-phase nitrogen abundances (N/H), 
resulting in high N/O ratios.  While their SFRs show that something has quenched 
their star formation, their stellar masses inform us that this is not due to any 
premature quenching mechanism.  The high nitrogen abundances in the green valley 
galaxies indicate that the galaxies are either no longer forming stars (since 
nitrogen is produced in lower mass stars than oxygen), or that the galaxies were 
able to produce both primary and secondary nitrogen (heavy elements were present 
during the last few star formation episodes to permit the CNO cycle to commence 
earlier).  This chemical abundance pattern (normal oxygen, high nitrogen, and 
high N/O ratio) is also seen in galaxies classified as AGN, indicating that the 
galaxies in the green valley may have an AGN.

There is a higher fraction of faint wall galaxies than faint void galaxies in 
the green valley.  In conjunction with the conclusions of \cite{Douglass17b} and 
\cite{Douglass17c}, this may indicate that void dwarf galaxies are less evolved 
than dwarf galaxies in denser environments.  It would be beneficial to 
investigate the small-scale ($\sim$1 \hMpc) environment of galaxies in the green 
valley, to determine if any interactions are responsible for their transitional 
state.
